Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-19 snapshot_system/fast14_deduplication.tex
modify

Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  From the above equations:
\[
\frac{N_1}{N_o}=  \frac{1-\sigma}{V_o}<1.
\] 
Thus when there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a lower chance to lose a snapshot than the VO approach because
$N_1<N_o$. 
Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
our test dataset.
%which shows how many VMs the failure of a single block can affect. 
For VC, we only show
the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
one VM.
From data, 
we have observed that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
Also if  the backup for multiple VMs were conducted concurrently, there would be more
VMs shared  by each file block on average in VO. 
%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.

>>>>

Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  From the above equations:
\[
\frac{N_1}{N_o} \approx  \frac{1-\sigma}{V_o}.
\]

Thus $N_1$ is much smaller than $N_o$. 
When there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a much lower chance to lose a snapshot than VO. 
Figure~\ref{fig:fsb-links} shows the average number of VMs sharing each file block from
our test dataset.
%which shows how many VMs the failure of a single block can affect. 
For VC, we only show
the sharing degree of  PDS-oriented file blocs  because non-PDS blocks always belong to
one VM.
From data, 
we have observed that $N_1 +N_2 < N_o$ in Figure~\ref{fig:vm-links}. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
Also if  the backup for multiple VMs were conducted concurrently, there would be more
VMs shared  by each file block on average in VO. 
%Therefore, even when there is a loss of a PDS block, the VC approach tolerates the fault better.
